Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-04 paper/paper.Rmd
more changes from @jbracher

---
title: Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble
preprint: true
author: 
  - name: Sam Abbott
    affiliation: 1
    corresponding: true
    email: sam.abbott@lshtm.ac.uk
  - name: Katharine Sherratt
    affiliation: 1
  - name: Nikos Bosse
    affiliation: 1
  - name: Hugo Gruson
    affiliation: 1
  - name:  Johannes Bracher
    affiliation: 2
  - name: Sebastian Funk
    affiliation: 1
affiliation:
  - code: 1
    address: London School of Hygiene and Tropical Medicine, London, UK
  - code: 2
    address: Chair of Statistics and Econometrics, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany
abstract: > 
  Multi-model and multi-team ensembles have become increasingly popular as an approach to increase the robustness and performance of infectious disease forecasts, especially during the COVID-19 pandemic. However, these forecasts require a coordinated team to produce and are effectively black boxes. In other fields, resource usage has been reduced by training simplified models that reproduce some of the observed behaviour of more complex models. 
  Here we use observations of the behaviour of the European COVID-19 Forecast Hub ensemble combined with our own forecasting experience, to specify a series of model assumptions modelling incident reported cases of COVID-19. We then develop a forecast model using these assumptions and compare its performance to the European forecast hub ensemble in real-time from the 15th of January 2022 to the 19th of July 2022 over a four-week forecast horizon using the weighted interval score.
  We found that this surrogate model performed visibly somewhat similarly to a subset of example locations though with increased uncertainty and poor performance at forecasting peak incidence. Unsurprisingly, we concluded that average performance was substantially worse relative to the ensemble forecast but that median performance was more comparable though still worse. The majority of the difference in performance was linked to a subset of forecasts with the majority of these being from early 2022. We note that despite performing worse than the hub ensemble the majority of the time our surrogate model showed better calibration, and was less liable to underpredict. The central part of the surrogate model’s forecast distribution performed more similarly to the ensemble forecast’s distribution but maintained a right skewed performance distribution.
  We conclude that our simplified forecast model may have captured some of the dynamics of the hub ensemble. However, more work needs to be done to understand the implicit epidemiological model that represents its behaviour and whether or not this is the optimal choice for stakeholders' requirements. We also conclude that our findings may be largely driven by the choice of evaluation measure used by the forecast hub. If the assumptions underlying this measure do not reflect forecast users' expectations then the forecast hub submissions may also not reflect these expectations. Our work is potentially useful for forecast consumers as a tool for understanding the inherent assumptions of the forecasts they are making use of and to researchers aiming to develop forecast approaches that perform similarly, or better than, current multi-model and multi-team forecast ensembles that are trusted by stakeholders.
bibliography: library.bib
output:
  bookdown::pdf_book:
    base_format: rticles::peerj_article
    extra_dependencies: ["float"]
---

@@

The trend towards large-scale multi-team ensemble forecasting in infectious diseases has accelerated during the COVID-19 pandemic due to a pressing need for reliable forecasts and a perception that many publicly available forecasts were low quality. Over 2020 and 2021, teams established COVID-19 Forecasting Hubs covering the US [@Cramer2022-sp], Germany and Poland [@Bracher2021-wk], and Europe [@Sherratt2022-ue] (all three including authors of this study). All of these collaborations ensembled contributions from multiple independent teams using a similar approach and have shown that their ensemble forecasts outperform most individually contributed forecasts whilst remaining generally robust to outliers in reporting.
Both the US and European forecast hubs were supported and received funding from, public health agencies (the Center for Disease Control (CDC) and European Center for Disease Prevention and Control (ECDC) respectively) with their forecasts being adopted into the official output from these agencies.
However, less progress has been made in mitigating the downsides of these projects and improving access to the high-quality and robust forecasts they seek to generate to geographies without coverage or for other infectious diseases.

In this work, we draw insights from ensemble forecasts produced and endorsed by these forecast hubs, as well as our forecasting work, to propose and evaluate a "surrogate" forecast model.
This seeks to mitigate some of the downsides of recent COVID-19 ensembles forecasts by emulating their observed behaviour, using a minimal set of easily communicated and epidemiologically justifiable assumptions, and limited computational resources with an easily generalised implementation.
The primary aim of this approach is to help highlight the behaviour, and potential mechanisms behind this behaviour, of ensemble forecast widely considered the gold standard for COVID-19 forecasting.
In addition to this, we seek to provide a simple, and robust, forecasting system that others can easily reuse, perhaps where a forecast hub ensemble is not available, and be used as a platform for future research both into improving understanding of ensemble behaviour and increased forecast performance.

@@

To understand the behaviour of the forecast hub ensembles we need to first explore the structure of the COVID-19 Forecast Hubs [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue].
These collaborations share a similar design with a central team running the hub, vetting forecasts, and producing the ensemble forecast as well as teams of independent forecast contributors who design their forecast models and then use them to produce a weekly forecast that they then submit to the central hub team. 
Each hub targets a range of metrics including test-positive reported cases, reported deaths, and hospitalisations has a specific geographic focus and asks for weekly forecasts (using epidemiological weeks i.e. Sunday to Saturday) over a time horizon of a few weeks.
Typically, the ensemble forecast produced each week comprises at least 3 independent forecasts using a range of approaches and is produced using an unweighted median ensemble [@Sherratt2022-ue].
Observed data are available and updated daily, and most submitted forecasts use this dataset, along with potentially other sources of real-time information, to produce forecasts.
Here, we focus on reported cases and primarily on the European forecast hub but our observations hold, in our view, across COVID-19 forecast hubs and to a lesser degree targets.
We focus on reported cases as these represent the most common forecast target for COVID-19 forecast models [@Nixon2022-zv], they are often of the most direct interest due to being a leading indicator, and they are generally the most challenging to predict.
In general, 5 main classes of forecast models are submitted [@Bracher2022-ug; @Cramer2022-sp], statistical forecasting models such as ARIMA models [@REF], mechanistic forecasting models based on the compartmental modelling framework and its generalisations [@REF], semi-mechanistic approaches that blend both of these approaches [@REF; @Bosse2022-hm], agent-based simulation models [@Rakowski2010-ft; @Adam2020-if], and human insight based forecast models that may also include elements of other methods [@Bosse2022-hm].
Real-time evaluation has shown that each of these classes of models may perform well depending on the context and specific implementation of the forecast model [@Bosse2022-hm].

@@

Unlike our epidemiologically motivated forecast submissions, the hub ensemble forecasts were typically robust to daily reporting artefacts. They also demonstrated some ability to forecast future changes in trends that were not present in the observed data similarly to our human insight forecasts indicating the likely inclusion of either human insight, or assumptions about future interventions. 
In general, in comparison to our submitted forecasts, the ensemble forecasts were more auto-correlated and less reactive to changes from stable or reducing case incidence to increasing incidence. On the other hand, this also meant that the ensemble was less likely to adopt short-term changes in incidence and hence produced better long-term forecasts. Finally, the ensemble forecast tended to produce sharper forecasts and have a tendency toward under vs over predicting. There is some suggestion that this was partially driven by the ensemble forecast having non-exponential uncertainty, unlike many infectious disease forecasting models

@@

In this study, we evaluate an initial attempt at a surrogate model to replicate the observed behaviour of current multi-team forecast ensembles based on a set of clear assumptions.
We submitted this model to the European Forecast Hub and here we evaluate its performance relative to the Hub ensemble.
First, we define the model and summarise its implementation, with a focus on minimal resource use and reproducibility, as a GitHub Actions workflow.  We briefly outline some of the summary statistics it produces and their epidemiological relevance.
We then evaluate its real-time performance in comparison to the European forecast hub ensemble by visualising forecasts, using the weighted interval score [@bracherEvaluatingEpidemicForecasts2021], a commonly used proper scoring rule, and quantifying the empirical coverage of the forecasts produced.
We attempt to highlight settings where this model performs well as a surrogate to the ensemble forecast and areas where more work is needed.  Finally, we summarise our findings, discuss their implications, and highlight areas where more work is needed.
We aim for this work to highlight some of the potential implicit assumptions of current COVID-19 forecast hub ensembles, provide a sensible, low-resource, surrogate model in settings where large-scale collaborative forecasting efforts are not possible, and provide inspiration for forecasters looking to make principled improvements to their models.

@@

The European forecast hub requests forecasts for one to four-week forecast horizon and requires forecasts to use a pre-specified format with 23 quantiles of the predictive probability distribution.
No restrictions were placed on who could submit forecasts and the hub team actively invited participation from research groups known to be involved with COVID-19 forecasting projects.
Forecasters used a wide range of forecasting methods including statistical approaches, mechanistic models including deterministic ordinary differential equation models and agent-based models, semi-mechanistic models, expert elicitation models, and ensembles of multiple approaches [@EuroHub].
Teams submitted forecasts at the latest two days after the complete dataset for the forecast week became available and were allowed to use all data available at the time of submission (i.e including up to two days of data for the current week). 
The ensemble forecast was constructed by taking the median of all predictive quantiles without the exclusion of any validly submitted forecast (where validity was defined as passing minimal formatting checks by the hub team and timely submission). 
An ensemble was only produced for locations with at least 3 independent forecast models including the hub baseline model.
Submitted forecasts and target observations are available from the European forecast hub GitHub repository [@EuroHubGitHub]. We provide code in the repository of this study to streamline access.

@@

We model the expectation ($\lambda_t$) of reported cases ($C_t$) as an order 1 autoregressive (AR(1)) process by epidemiological week ($t$) on the log scale.
The model is initialised by assuming that the initially reported cases are representative with a small amount of error (2.5%).
We assume a negative binomial observation model with overdispersion $\phi$ for reported cases ($C_t$).

@@

We evaluate forecasts for all locations and horizons quantitatively using the absolute error (AE) of the median forecast and the weighted interval score (WIS) [@bracherEvaluatingEpidemicForecasts2021].
The WIS is a quantile-based proper scoring rule that approximates the continuous ranked probability score (CRPS).
Both the WIS and CRPS are generalisations of the absolute error to evaluate probabilistic forecasts and are widely used to evaluate COVID-19 forecasts, including by the European forecast hub [@Sherratt2022-ue].
We present WIS for the subset of forecasts we explore visually for both the ensemble and surrogate model by date and forecast horizon (1 and 4 weeks).

@@

`r nrow(anomalies)` observations, stratified by week and location, were defined to be anomalous within the study period by the European forecast hub [@EuroHub]. 
Forecasts for these observations were excluded as were forecasts for forecast weeks where they were the latest available data.
Data anomalies were not randomly distributed with some locations being particularly prone to data revisions including Lithuania (with `r anomalies[location == "LT", .N]` weeks with data anomalies), and Portugal (with `r anomalies[location == "PT", .N]` weeks with data anomalies).
Anomalies were also not evenly distributed over time with a higher proportion occurring earlier in the study period (potentially due to our choice to extract data from the 1st of September which effectively truncated anomalies).
`r per_excluded`% of forecasts were excluded across all horizons due to anomalies in the observed data. Aggregated across horizons `r exclusions$per`% of forecasts included at least one week with anomalous data.

@@

```{r vis-forecasts, fig.cap = "a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one and four weeks). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time. b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

@@

```{r assemble-eval, fig.height = 12, fig.width = 12, out.width = "95%", fig.cap = "Relative weighted interval score by location, horizon, and forecast date for the surrogate forecast model compared to the ensemble forecast model on the log scale. a.) The density of the relative score by horizon. Horizontal black lines give the 5\\%, 35\\%, 65\\%, and 95\\% quantiles. b.) The density of the relative score by month for a given forecast horizon stratified by the one and four-week forecast horizon. c.) The average relative weighted interval score and absolute error for the surrogate model compared to the ensemble forecast by forecast horizon. d.) The density of the relative score by forecast location stratified by the one and four-week forecast horizon. The dashed line on all plots indicates when the ensemble forecast is equivalent to the surrogate forecast. The vertical black lines on the y-axis give individual relative scores."}
p <- (
  (
    (
      plot_rwis_horizon / plot_rwis_by_month
    )  +
    plot_layout(heights = c(4, 5), guides = "collect")
  ) |
  (
    (
      plot_relative_summary(relative_summary) +
      plot_layout(guides = "keep")
    ) +
    plot_rwis_location +
    plot_layout(heights = c(1, 7), guides = "collect")
  )
) +
  plot_layout(guides = "collect", widths = c(1, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%", fig.cap = "a.) Empirical coverage of the surrogate and ensemble forecasts at the 90\\%, 60\\%, and 30\\% prediction intervals stratified by forecast horizon. Ideally, a well-calibrated forecast should have empirical coverage for a given prediction interval that equals the nominal level of the interval (i.e., 30\\%, 60\\% and 90\\%, respectively). b.) Empirical coverage by quantile for both the surrogate and ensemble forecasts. A well-calibrated forecast should have empirical quantiles that match the theoretical ones. The green area of this figure corresponds to conservative forecasts. c.) Median relative weighted interval score by quantile and forecast horizon for the surrogate forecast compared to the ensemble forecast. d.) Bias of the ensemble and surrogate forecasts stratified by horizon."}
p <- (
  (
    (
      plot_coverage_range(coverage, ranges)
    )
  ) | (
    plot_coverage_quantiles(scores) + (
      plot_rel_score_by_quantile(relative_interval_score) +
      plot_bias(summary_performance)
    ) +
    plot_layout(heights = c(2, 1), guides = "collect")
  )
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

@@

In this study, we defined a surrogate model aiming to replicate some of the observed behaviour of the European forecast hub multi-team ensemble for forecasting test-positive reported COVID-19 cases in European nations.
We first defined a set of assumptions for how the surrogate model should behave based on our observations of the European forecast hub ensemble, and our experience submitting forecasts to various forecast hubs.
We aimed for a model that could be easily understood, that produced epidemiologically meaningful summary statistics, and that could be run with low compute resources.
We further provide a fully reproducible workflow for running and evaluating this model using GitHub actions facilitating others to do the same.

Over the 6 months of the study period, we found that our surrogate model produced forecasts that were visually similar to those from the forecast hub ensemble on the log scale though with greater uncertainty.
Visual differences were more marked on the natural scale with the surrogate model forecasting spuriously high peak incidence.
In a subset of example locations, we observed some variation in performance across locations, that the ensemble better-captured peak incidence, and that the surrogate model appeared biased toward overprediction.
Evaluating the relative performance of the surrogate model compared to the European forecast hub ensemble we found that the mean performance was substantially worse and that relative performance decreased with the forecast horizon.
The median forecast performance of the surrogate model was also worse when compared to forecasts from the ensemble though the majority of surrogate forecasts were within 50% of the performance observed for the ensemble forecast.
The difference in mean and median relative performance suggested a skewed distribution in scores, which we confirmed visually. 
This means that a relatively small fraction of forecasts were responsible for a substantial portion of the difference in performance.
Evaluating point forecast performance indicated a similar pattern of performance as that observed using the full predictive distribution though the relative performance of the surrogate model generally improved.
Performance varied by location and forecast date with the surrogate model performing worse in the first part of 2022 which may have been linked to incidence rates peaking across forecast locations linked to the spread of BA.2.
In general, the relative performance of the surrogate model degraded as forecast horizons increased with the distribution of relative performance having an increasingly heavy right tail as the forecast horizon increased indicating a greater share of forecasts performing very poorly in comparison to the hub ensemble.
The forecast hub ensemble was poorly calibrated, particularly at longer forecast horizons and larger prediction intervals, compared to the surrogate model though the surrogate model tended to be overly uncertain at large intervals.
The ensemble forecast was biased towards under prediction at short to medium forecast horizons but unbiased at longer horizons. 
In comparison, the surrogate model was biased towards over prediction and this bias increased linearly with the forecast horizon.

@@

Our study benefits from having been conducted using forecasts produced in real-time, rather than retrospectively, and submitted to an independent forecast research hub (though we note the overlap between authors on this study and the European forecast hub [@Sherratt2022-ue]).

@@

Given the number of forecasts submitted in most locations and the European forecast hubs' practice of not calculating an ensemble when fewer than 3 independent forecasts were available, the bias in our results caused by this limitation should be relatively small.
Importantly in this study, we focussed on replicating the forecast hub ensembles' observed behaviour rather than attempting to define an optimal forecast for forecast consumers.

@@

However, if we start from the view that the forecast hub ensemble has traits that are desirable for use by policy-makers (i.e robustness and good average performance), which can be found widely in the literature [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue], then our approach may make sense as a way of producing a "good" forecast.

>>>>

---
title: Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble
preprint: true
author: 
  - name: Sam Abbott
    affiliation: 1
    corresponding: true
    email: sam.abbott@lshtm.ac.uk
  - name: Katharine Sherratt
    affiliation: 1
  - name: Nikos Bosse
    affiliation: 1
  - name: Hugo Gruson
    affiliation: 1
  - name:  Johannes Bracher
    affiliation: 2
  - name: Sebastian Funk
    affiliation: 1
affiliation:
  - code: 1
    address: London School of Hygiene and Tropical Medicine, London, UK
  - code: 2
    address: Chair of Statistics and Econometrics, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany
abstract: > 
  Multi-model and multi-team ensembles have become increasingly popular as an approach to increase the robustness and performance of infectious disease forecasts, especially during the COVID-19 pandemic. However, these forecasts require a coordinated team to produce and are effectively black boxes. In other fields, resource usage has been reduced by training simplified models that reproduce some of the observed behaviour of more complex models. 
  Here we use observations of the behaviour of the European COVID-19 Forecast Hub ensemble combined with our own forecasting experience, to specify a series of model assumptions modelling incident reported cases of COVID-19. We then develop a forecast model using these assumptions and compare its performance to the European Forecast Hub ensemble in real-time from the 15th of January 2022 to the 19th of July 2022 over a four-week forecast horizon using the weighted interval score.
  We found that this surrogate model performed visibly somewhat similarly to a subset of example locations though with increased uncertainty and poor performance at forecasting peak incidence. Unsurprisingly, we concluded that average performance was substantially worse relative to the ensemble forecast but that median performance was more comparable though still worse. The majority of the difference in performance was linked to a subset of forecasts with the majority of these being from early 2022. We note that despite performing worse than the hub ensemble the majority of the time our surrogate model showed better calibration, and was less liable to underpredict. The central part of the surrogate model’s forecast distribution performed more similarly to the ensemble forecast’s distribution but maintained a right skewed performance distribution.
  We conclude that our simplified forecast model may have captured some of the dynamics of the hub ensemble. However, more work needs to be done to understand the implicit epidemiological model that represents its behaviour and whether or not this is the optimal choice for stakeholders' requirements. We also conclude that our findings may be largely driven by the choice of evaluation measure used by the Forecast Hub. If the assumptions underlying this measure do not reflect forecast users' expectations then the Forecast Hub submissions may also not reflect these expectations. Our work is potentially useful for forecast consumers as a tool for understanding the inherent assumptions of the forecasts they are making use of and to researchers aiming to develop forecast approaches that perform similarly, or better than, current multi-model and multi-team forecast ensembles that are trusted by stakeholders.
bibliography: library.bib
output:
  bookdown::pdf_book:
    base_format: rticles::peerj_article
    extra_dependencies: ["float"]
---

@@

The trend towards large-scale multi-team ensemble forecasting in infectious diseases has accelerated during the COVID-19 pandemic due to a pressing need for reliable forecasts and a perception that many publicly available forecasts were low quality. Over 2020 and 2021, teams established COVID-19 Forecasting Hubs covering the US [@Cramer2022-sp], Germany and Poland [@Bracher2021-wk], and Europe [@Sherratt2022-ue] (all three including authors of this study). All of these collaborations ensembled contributions from multiple independent teams using a similar approach and have shown that their ensemble forecasts outperform most individually contributed forecasts whilst remaining generally robust to outliers in reporting.
Both the US and European Forecast Hubs were supported and received funding from public health agencies (the Center for Disease Control (CDC) and European Center for Disease Prevention and Control (ECDC) respectively) with their forecasts being adopted into the official output from these agencies.
However, less progress has been made in mitigating the downsides of these projects and improving access to the high-quality and robust forecasts they seek to generate to geographies without coverage or for other infectious diseases.

In this work, we draw insights from ensemble forecasts produced and endorsed by these Forecast Hubs, as well as our forecasting work, to propose and evaluate a "surrogate" forecast model.
This seeks to mitigate some of the downsides of recent COVID-19 ensembles forecasts by emulating their observed behaviour, using a minimal set of easily communicated and epidemiologically justifiable assumptions, and limited computational resources with an easily generalised implementation.
The primary aim of this approach is to help highlight the behaviour, and potential mechanisms behind this behaviour, of ensemble forecast widely considered the gold standard for COVID-19 forecasting.
In addition to this, we seek to provide a simple, and robust, forecasting system that others can easily reuse, perhaps where a Forecast Hub ensemble is not available, and be used as a platform for future research both into improving understanding of ensemble behaviour and increased forecast performance.

@@

To understand the behaviour of the Forecast Hub ensembles we need to first explore the structure of the COVID-19 Forecast Hubs [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue].
These collaborations share a similar design with a central team running the hub, vetting forecasts, and producing the ensemble forecast as well as teams of independent forecast contributors who design their forecast models and then use them to produce a weekly forecast that they then submit to the central hub team. 
Each hub targets a range of metrics including test-positive reported cases, reported deaths, and hospitalisations has a specific geographic focus and asks for weekly forecasts (using epidemiological weeks i.e. Sunday to Saturday) over a time horizon of a few weeks.
Typically, the ensemble forecast produced each week comprises at least 3 independent forecasts using a range of approaches and is produced using an unweighted median ensemble [@Sherratt2022-ue].
Observed data are available and updated daily, and most submitted forecasts use this dataset, along with potentially other sources of real-time information, to produce forecasts.
Here, we focus on reported cases and primarily on the European Forecast Hub but our observations hold, in our view, across COVID-19 Forecast Hubs and to a lesser degree targets.
We focus on reported cases as these represent the most common forecast target for COVID-19 forecast models [@Nixon2022-zv], they are often of the most direct interest due to being a leading indicator, and they are generally the most challenging to predict.
In general, 5 main classes of forecast models are submitted [@Bracher2022-ug; @Cramer2022-sp], statistical forecasting models such as ARIMA models [@REF], mechanistic forecasting models based on the compartmental modelling framework and its generalisations [@REF], semi-mechanistic approaches that blend both of these approaches [@REF; @Bosse2022-hm], agent-based simulation models [@Rakowski2010-ft; @Adam2020-if], and human insight based forecast models that may also include elements of other methods [@Bosse2022-hm].
Real-time evaluation has shown that each of these classes of models may perform well depending on the context and specific implementation of the forecast model [@Bosse2022-hm].

@@

Unlike our epidemiologically motivated forecast submissions, the hub ensemble forecasts were typically robust to daily reporting artefacts. They also demonstrated some ability to forecast future changes in trends that were not present in the observed data similarly to our human insight forecasts indicating the likely inclusion of either human insight, or assumptions about future interventions. 
In comparison to our submitted forecasts, the ensemble forecasts were less reactive to changes in trend such as from stable or reducing case incidence to increasing incidence. On the other hand, this also meant that the ensemble was less likely to adopt short-term changes in incidence and hence produced better long-term forecasts. Finally, the ensemble forecast tended to produce sharper forecasts and have a tendency toward under vs over predicting. There is some suggestion that this was partially driven by the ensemble forecast having non-exponential uncertainty, unlike many infectious disease forecasting models

@@

In this study, we evaluate an initial attempt at a surrogate model to replicate the observed behaviour of current multi-team forecast ensembles based on a set of clear assumptions.
We submitted this model to the European Forecast Hub and here we evaluate its performance relative to the Hub ensemble.
First, we define the model and summarise its implementation, with a focus on minimal resource use and reproducibility, as a GitHub Actions workflow.  We briefly outline some of the summary statistics it produces and their epidemiological relevance.
We then evaluate its real-time performance in comparison to the European Forecast Hub ensemble by visualising forecasts, using the weighted interval score [@bracherEvaluatingEpidemicForecasts2021], a commonly used proper scoring rule, and quantifying the empirical coverage of the forecasts produced.
We attempt to highlight settings where this model performs well as a surrogate to the ensemble forecast and areas where more work is needed.  Finally, we summarise our findings, discuss their implications, and highlight areas where more work is needed.
We aim for this work to highlight some of the potential implicit assumptions of current COVID-19 Forecast Hub ensembles, provide a sensible, low-resource, surrogate model in settings where large-scale collaborative forecasting efforts are not possible, and provide inspiration for forecasters looking to make principled improvements to their models.

@@

The European Forecast Hub requests forecasts for one to four-week forecast horizon and requires forecasts to use a pre-specified format with 23 quantiles of the predictive probability distribution.
No restrictions were placed on who could submit forecasts and the hub team actively invited participation from research groups known to be involved with COVID-19 forecasting projects.
Forecasters used a wide range of forecasting methods including statistical approaches, mechanistic models including deterministic ordinary differential equation models and agent-based models, semi-mechanistic models, expert elicitation models, and ensembles of multiple approaches [@EuroHub; @Bracher2022-ug; @Cramer2022-sp].
Teams submitted forecasts at the latest two days after the complete dataset for the forecast week became available and were allowed to use all data available at the time of submission (i.e including up to two days of data for the current week). 
The ensemble forecast was constructed by taking the median of all predictive quantiles without the exclusion of any validly submitted forecast (where validity was defined as passing minimal formatting checks by the hub team and timely submission). 
An ensemble was only produced for locations with at least 3 independent forecast models including the hub baseline model.
Submitted forecasts and target observations are available from the European Forecast Hub GitHub repository [@EuroHubGitHub]. We provide code in the repository of this study to streamline access.

@@

We model the expectation ($\lambda_t$) of reported cases ($C_t$) given past reported cases as an order 1 autoregressive (AR(1)) process by epidemiological week ($t$) on the log scale.
The model is initialised by assuming that the initially reported cases are representative with a small amount of error (2.5%).
We assume a negative binomial observation model with overdispersion $\phi$ for reported cases ($C_t$).

@@

We evaluate forecasts for all locations and horizons quantitatively using the absolute error (AE) of the median forecast and the weighted interval score (WIS) [@bracherEvaluatingEpidemicForecasts2021].
The WIS is a quantile-based proper scoring rule that approximates the continuous ranked probability score (CRPS).
Both the WIS and CRPS are generalisations of the absolute error to evaluate probabilistic forecasts and are widely used to evaluate COVID-19 forecasts, including by the European Forecast Hub [@Sherratt2022-ue].
We present WIS for the subset of forecasts we explore visually for both the ensemble and surrogate model by date and forecast horizon (1 and 4 weeks).

@@

`r nrow(anomalies)` observations, stratified by week and location, were defined to be anomalous within the study period by the European Forecast Hub [@EuroHub]. 
Forecasts for these observations were excluded as were forecasts for forecast weeks where they were the latest available data.
Data anomalies were not randomly distributed with some locations being particularly prone to data revisions including Lithuania (with `r anomalies[location == "LT", .N]` weeks with data anomalies), and Portugal (with `r anomalies[location == "PT", .N]` weeks with data anomalies).
Anomalies were also not evenly distributed over time with a higher proportion occurring earlier in the study period (potentially due to our choice to extract data from the 1st of September which effectively truncated anomalies).
`r per_excluded`% of forecasts were excluded across all horizons due to anomalies in the observed data. Aggregated across horizons `r exclusions$per`% of forecasts included at least one week with anomalous data.

@@

```{r vis-forecasts, fig.cap = "a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one and four weeks). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time. b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 15)
  )
suppressWarnings(print(p))
```

@@

```{r assemble-eval, fig.height = 12, fig.width = 12, out.width = "95%", fig.cap = "Relative weighted interval score by location, horizon, and forecast date for the surrogate forecast model compared to the ensemble forecast model on the log scale. a.) The density of the relative score by horizon. Horizontal black lines give the 5\\%, 35\\%, 65\\%, and 95\\% quantiles. b.) The density of the relative score by month for a given forecast horizon stratified by the one and four-week forecast horizon. c.) The average relative weighted interval score and absolute error for the surrogate model compared to the ensemble forecast by forecast horizon. d.) The density of the relative score by forecast location stratified by the one and four-week forecast horizon. The dashed line on all plots indicates when the ensemble forecast is equivalent to the surrogate forecast. The vertical black lines on the y-axis give individual relative scores."}
p <- (
  (
    (
      plot_rwis_horizon / plot_rwis_by_month
    )  +
    plot_layout(heights = c(4, 5), guides = "collect")
  ) |
  (
    (
      plot_relative_summary(relative_summary) +
      plot_layout(guides = "keep")
    ) +
    plot_rwis_location +
    plot_layout(heights = c(1, 7), guides = "collect")
  )
) +
  plot_layout(guides = "collect", widths = c(1, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 15)
  )
suppressWarnings(print(p))
```

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%", fig.cap = "a.) Empirical coverage of the surrogate and ensemble forecasts at the 90\\%, 60\\%, and 30\\% prediction intervals stratified by forecast horizon. Ideally, a well-calibrated forecast should have empirical coverage for a given prediction interval that equals the nominal level of the interval (i.e., 30\\%, 60\\% and 90\\%, respectively). b.) Empirical coverage by quantile for both the surrogate and ensemble forecasts. A well-calibrated forecast should have empirical quantiles that match the theoretical ones. The green area of this figure corresponds to conservative forecasts. c.) Median relative weighted interval score by quantile and forecast horizon for the surrogate forecast compared to the ensemble forecast. d.) Bias of the ensemble and surrogate forecasts stratified by horizon."}
p <- (
  (
    (
      plot_coverage_range(coverage, ranges)
    )
  ) | (
    plot_coverage_quantiles(scores) + (
      plot_rel_score_by_quantile(relative_interval_score) +
      plot_bias(summary_performance)
    ) +
    plot_layout(heights = c(2, 1), guides = "collect")
  )
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 15)
  )
suppressWarnings(print(p))
```

@@

In this study, we defined a surrogate model aiming to replicate some of the observed behaviour of the European Forecast Hub multi-team ensemble for forecasting test-positive reported COVID-19 cases in European nations.
We first defined a set of assumptions for how the surrogate model should behave based on our observations of the European Forecast Hub ensemble, and our experience submitting forecasts to various Forecast Hubs.
We aimed for a model that could be easily understood, that produced epidemiologically meaningful summary statistics, and that could be run with low compute resources.
We further provide a fully reproducible workflow for running and evaluating this model using GitHub actions facilitating others to do the same.

Over the 6 months of the study period, we found that our surrogate model produced forecasts that were visually similar to those from the Forecast Hub ensemble on the log scale though with greater uncertainty.
Visual differences were more marked on the natural scale with the surrogate model forecasting spuriously high peak incidence.
In a subset of example locations, we observed some variation in performance across locations, that the ensemble better-captured peak incidence, and that the surrogate model appeared biased toward overprediction.
Evaluating the relative performance of the surrogate model compared to the European Forecast Hub ensemble we found that the mean performance was substantially worse and that relative performance decreased with the forecast horizon.
The median forecast performance of the surrogate model was also worse when compared to forecasts from the ensemble though the majority of surrogate forecasts were within 50% of the performance observed for the ensemble forecast.
The difference in mean and median relative performance suggested a skewed distribution in scores, which we confirmed visually. 
This means that a relatively small fraction of forecasts were responsible for a substantial portion of the difference in performance.
Evaluating point forecast performance indicated a similar pattern of performance as that observed using the full predictive distribution though the relative performance of the surrogate model generally improved.
Performance varied by location and forecast date with the surrogate model performing worse in the first part of 2022 which may have been linked to incidence rates peaking across forecast locations linked to the spread of BA.2.
In general, the relative performance of the surrogate model degraded as forecast horizons increased with the distribution of relative performance having an increasingly heavy right tail as the forecast horizon increased indicating a greater share of forecasts performing very poorly in comparison to the hub ensemble.
The Forecast Hub ensemble was poorly calibrated, particularly at longer forecast horizons and larger prediction intervals, compared to the surrogate model though the surrogate model tended to be overly uncertain at large intervals.
The ensemble forecast was biased towards under prediction at short to medium forecast horizons but unbiased at longer horizons. 
In comparison, the surrogate model was biased towards over prediction and this bias increased linearly with the forecast horizon.

@@

Our study benefits from having been conducted using forecasts produced in real-time, rather than retrospectively, and submitted to an independent forecast research hub (though we note the overlap between authors on this study and the European Forecast Hub [@Sherratt2022-ue]).

@@

Given the number of forecasts submitted in most locations and the European Forecast Hubs' practice of not calculating an ensemble when fewer than 3 independent forecasts were available, the bias in our results caused by this limitation should be relatively small.
Importantly in this study, we focussed on replicating the Forecast Hub ensembles' observed behaviour rather than attempting to define an optimal forecast for forecast consumers.

@@

However, if we start from the view that the Forecast Hub ensemble has traits that are desirable for use by policy-makers (i.e robustness and good average performance), which can be found widely in the literature [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue], then our approach may make sense as a way of producing a "good" forecast.
